\section{Protocol Details}

\tikzstyle{block} = [rectangle, fill=maincolor!80, text=backgroundcolor, minimum height=1cm, minimum width=2cm]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Timekeeper Protocol
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Timekeeper Protocol} \centering
    \input{content/protocol-details/protocol-fig}

    \begin{itemize}
        \item<2-> All events are triggered by parties' local clocks.
        \item<3-> Parties use 2-for-1 PoW to mine and emit synchronization beacons to sync their local clocks.
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% A New Timestamp Scheme
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{A New Timestamp Scheme}
    We extend the timestamp scheme from $\langle time \rangle$ to $\langle interval, time \rangle$.

    \centering \input{content/protocol-details/timestamp-scheme}

    \begin{itemize}
        \item<2-> Chain should include monotonically increasing timestamps.
        \item<3-> Recalibration may ``rewind'' local clocks.
        \item<4-> Easy to distinguish the epoch of blocks mined at the boundary.
        \item<5-> After setting clocks backwards, it is unreasonable to let honest parties stop mining.
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% A New Target Recalculation Function
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
    \frametitle{A New Target Recalculation Function}

    We reverse Bitcoin's target recalculation function.
    \vspace*{1em}

    \begin{columns}[c, onlytextwidth]
        \begin{column}{0.45\textwidth}<2-> \centering
            \emph{Bitcoin's Function} \vspace*{1em}
        \end{column}
        \begin{column}{0.45\textwidth}<3-> \centering
            \emph{Our New Function} \vspace*{1em}
        \end{column}
    \end{columns}

    \begin{columns}[c, onlytextwidth]
        \begin{column}{0.45\textwidth}<2->
            \input{content/protocol-details/bitcoin-func}
        \end{column}

        \begin{column}{0.1\textwidth}<3-> \centering
            \hspace*{.5em}
            \begin{tikzpicture}
                \draw[line width = .5em, ->,>=stealth,maincolor] (0, 0) -- (3em, 0);
            \end{tikzpicture}
            \vspace*{.2em}
        \end{column}

        \begin{column}{0.45\textwidth}<3->
            \input{content/protocol-details/new-func}
        \end{column}
    \end{columns}

    \begin{columns}[c, onlytextwidth]
        \footnotesize
        \begin{column}{0.45\textwidth}<2-> \centering
            \[ Target(K'') = Target(K) * \frac{K'.timestamp - K.timestamp}{\varLambda}. \]

            $\varLambda$ : ideal epoch duration (2 weeks in use)
        \end{column}

        \begin{column}{0.45\textwidth}<3-> \centering
            \[ Target(K') = Target(K) * \frac{\varLambda}{(\# \text{ of blocks in } K)}. \]

            $\varLambda$ : ideal \# of blocks an epoch
        \end{column}
    \end{columns}

    \vspace{1em}
    \uncover<4->{\centering \large
        No timestamp is needed in the new function!
    }

    \note[item]{Thank the audience for being awake.}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Synchronization Intervals
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
    \frametitle{Synchronization Intervals}

    A synchronization interval consists of 3 phases.

    \centering \input{content/protocol-details/interval-fig}

    \begin{enumerate}
        \item<2-> \emph{View convergence:} Wait for a consistent view of the last interval.
        \item<3-> \emph{Mining, inclusion and bookkeeping:} Use \Emph{2-for-1 PoW} to mine and diffuse beacons -- a tiny block that contains local time; honest parties bookkeep the arrival time of beacons.
        \item<4-> \emph{Beacon Convergence:} Wait for a consistent view of the beacons in current interval.
    \end{enumerate}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Local Adjustment
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
    \frametitle{Local Adjustment} 

    Parties adjust their clocks locally, based on the arrival time book and the on-chain info, by adding the \emph{median} of their difference to local time.
    \uncover<2->{
        \begin{equation*}
            \mathsf{shift} = \mathsf{median} \{\mathtt{SB}.timestamp - \mathtt{SB}.arrivalTime \mathbin| \mathtt{SB} \text{ in beacon set} \}
        \end{equation*}
    }

    \uncover<3->{ \centering \input{content/protocol-details/adjustment-fig} }
\end{frame}
